### 2025-01-05 sections/1-introduction.tex
more ref fixes

Recent $k$-nearest neighbor search algorithms designed to scale with the exponential growth of data include Hierarchical Navigable Small World networks (HNSW)~\cite{Malkov2016EfficientAR}, InVerted File indexing (FAISS-IVF)~\cite{faissivf}, random projection and tree building (ANNOY)~\cite{annoy}, and entropy-scaling search~\cite{yu2015entropy, ishaq2019clustered}. However, some of these algorithms do not provide exact search (as defined in Section \ref{sec:introduction} above).

Hierarchical Navigable Small World networks~\cite{Malkov2016EfficientAR} relies on navigable small world (NSW) networks~\cite{kleinberg2000navigation, boguna2009navigability} and skip lists.
HNSW builds a multi-layered graph of the dataset.
A query point and each data point are inserted into the graph and joined by an edge to the $M$ nearest nodes in the in the graph, where $M$ is a tunable parameter.
The highest layer in which an element can be placed is determined randomly with an exponentially-decaying probability distribution.
Search starts at the highest layer and descends to the lowest layer, greedily following a path of edges to the nearest node, until reaching the query point.
To improve accuracy, the $efSearch$ hyperparameter can be changed to specify the number of closest nearest neighbors to the query vector to be found at each layer.

>>>>

Recent $k$-nearest neighbor search algorithms designed to scale with the exponential growth of data include Hierarchical Navigable Small World networks (HNSW)~\cite{malkov2016hnsw}, InVerted File indexing (FAISS-IVF)~\cite{faissivf}, random projection and tree building (ANNOY)~\cite{annoy}, and entropy-scaling search~\cite{yu2015entropy, ishaq2019clustered}. However, some of these algorithms do not provide exact search (as defined in Section \ref{sec:introduction} above).

Hierarchical Navigable Small World networks~\cite{malkov2016hnsw} relies on navigable small world (NSW) networks~\cite{kleinberg2000navigation, boguna2009navigability} and skip lists.
HNSW builds a multi-layered graph of the dataset.
A query point and each data point are inserted into the graph and joined by an edge to the $M$ nearest nodes in the in the graph, where $M$ is a tunable parameter.
The highest layer in which an element can be placed is determined randomly with an exponentially-decaying probability distribution.
Search starts at the highest layer and descends to the lowest layer, greedily following a path of edges to the nearest node, until reaching the query point.
To improve accuracy, the $efSearch$ hyperparameter can be changed to specify the number of closest nearest neighbors to the query vector to be found at each layer.

### 2025-01-05 sections/3-datasets.tex
reference fixes
more ref fixes

We benchmark on a variety of datasets from the ANN-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}.
Table~\ref{tab:datasets:summary} summarizes these datasets.
The benchmarks for Fashion-Mnist, Glove-25, Sift, and Random (and for their synthetic augmentations) were conducted on an Amazon AWS (EC2) \texttt{r6i.16xlarge} instance, with a 64-core Intel Xeon Platinum 8375C CPU 2.90GHz processor, 512GB RAM.
This is the same configuration used in~\cite{Aumller2018ANNBenchmarksAB}.
The OS kernel was Ubuntu 22.04.3-Ubuntu SMP.
The Rust compiler was Rust 1.72.0, and the Python interpreter version was 3.9.16.
The benchmarks for SILVA and RadioML were conducted on an Intel Xeon E5-2690 v4 CPU @ 2.60GHz with 512GB RAM.
The OS kernel was Manjaro Linux 5.15.130-1-MANJARO.
The Rust compiler was Rust 1.72.0, and the Python interpreter version was 3.9.16.

>>>>

We benchmark on a variety of datasets from the ANN-benchmarks suite~\cite{aumuller2020ann}.
Table~\ref{tab:datasets:summary} summarizes these datasets.
The benchmarks for Fashion-Mnist, Glove-25, Sift, and Random (and for their synthetic augmentations) were conducted on an Amazon AWS (EC2) \texttt{r6i.16xlarge} instance, with a 64-core Intel Xeon Platinum 8375C CPU 2.90GHz processor, 512GB RAM.
This is the same configuration used in~\cite{aumuller2020ann}.
The OS kernel was Ubuntu 22.04.3-Ubuntu SMP.
The Rust compiler was Rust 1.72.0, and the Python interpreter version was 3.9.16.
The benchmarks for SILVA and RadioML were conducted on an Intel Xeon E5-2690 v4 CPU @ 2.60GHz with 512GB RAM.
The OS kernel was Manjaro Linux 5.15.130-1-MANJARO.
The Rust compiler was Rust 1.72.0, and the Python interpreter version was 3.9.16.
